### 2020-04-22 doc/manuscript/manuscript.Rmd
started manuscript doc

---
title: ""
output: pdf_document
---
**Title:** Tree growth and woody productivity are optimized under long-term mean climate conditions in forests worldwide

@@

\newpage

@@

>>>>

---
title: ""
output: word_document
---
**Title:** Tree growth and woody productivity(?) are optimized under long-term mean climate conditions in forests worldwide (*if this holds!*)

@@

\newline
\newline
\newline
\newline

# ABSTRACT

# MAIN

@@

# NOTES
